---
title: "Plotly Page"
output: 
  html_document:
    toc: true
    toc_float: true
---


In this page, we are going to make some plotly plots.

## Load package and data

```{r}
library(tidyverse)
library(p8105.datasets)

library(plotly)
```

## select the columns that we will use

```{r}
data(instacart)

instacart <- 
  instacart %>%
  janitor::clean_names() %>% 
  select(
    add_to_cart_order, reordered, user_id, order_dow, order_hour_of_day, days_since_prior_order, product_name, aisle, department)
instacart
```

## Boxplot

"Fruits are reordered more frequently than vegetables"

```{r}
instacart %>% 
  select(days_since_prior_order, product_name, aisle, department) %>% 
  filter(department == "produce") %>% 
  group_by(product_name) %>% 
  summarize(interval_time = mean(days_since_prior_order), aisle) %>% 
  distinct() %>% 
  plot_ly(y = ~interval_time, color = ~aisle, type = "box", colors = "viridis") 
```
+ labs(
    title = "Product Average Order Interval Time Distribution In Different Aisle",
    x = "Different Aisle",
    y = "Product Average Order Interval Time",
  )
  
## Barplot

"Healthier snacks tend to be purchased earlier in the day"

```{r}
instacart %>% 
  select(order_hour_of_day, product_name, aisle, department) %>% 
  filter(department == "snacks") %>% 
  group_by(product_name) %>% 
  summarize(mean_hour = mean(order_hour_of_day), product_name, aisle) %>% 
  distinct() %>% 
  plot_ly(x = ~product_name, y = ~mean_hour, color = ~aisle, type = "bar", colors = "viridis")
```

# Scatterplot